---
title: "Cross-validation Report"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Data input
```{r time of analysis, echo=FALSE, comment=NA, include=FALSE}
TIME <- analysis_time()
print(TIME)
```

```{r names of methods, echo = FALSE, comment=NA, include=FALSE}
method1 <- naam1()
method2 <- naam2()
```

In this cross-validation report the bioanalytical methods  `r method1` and `r method2` are compared to each other. The cross-validation was performed on `r TIME`. The observations included in this cross-validation are reported below: 

```{R data input, echo = FALSE, comment = NA}
DF <- datainput()
print(DF)
```

#Blant-Altman plot
```{r bland-altman plot, echo=FALSE, comment=NA}
plot(plot_BA())
```

#Blant-Altman statistics 
Number of samples used in the analysis: 
```{r number of samples, echo=FALSE, comment=NA}
print(nobs())
```

Descriptive statistics of the included samples:
```{r descriptive statistics, echo=FALSE, comment=NA}
print(sum_stat())
```

Confidence of Bland-Altman parameters
```{r confidence interval, echo=FALSE, comment=NA}
print(precision_sum())
```

##Passing-Bablok regression
Passing-Bablock plot
```{r PB plot, echo=FALSE, comment = NA}
plot(plot_PB())
```

#Passing-Bablock statistics 
Number of samples used in the analysis:
```{r number of samples PB, echo=FALSE, comment = NA}
print(nobs())
```

Descriptive statistics of the included samples:
```{r descriptive statistics PB, echo=FALSE, comment = NA}
print(sum_PB())
```

Passing-Bablock equation
```{r equation PB, echo=FALSE, comment = NA}
print(formule())
```

Confidence of Passing-Bablock fit
```{r confidence PB, echo=FALSE, comment=NA}
print(ci_pb())
```
